Wigglyhedra

### 2024-06-09 draft/wigglyhedra.tex
Started writing about t-structure.

\end{definition}
Let \(\mathcal{A}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) that is closed under isomorphism, which contains all the linear complexes.
\begin{proposition}\label{prop:standard-heart}
  The category \(\mathcal{A}_m\) is abelian.
  Furthermore, it is the heart of a bounded \(t\)-structure on \(\mathcal{C}_m\), which we call the \emph{standard \(t\)-structure} on \(\mathcal{C}_m\).
\end{proposition}
\asilata{Find a reference for this and possibly a cleaner statement.}

>>>>

\end{definition}
Let \(\mathcal{A}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) that is closed under isomorphism, which contains all the linear complexes.
For any integer \(N\), let \(\mathcal{C}_m^{\le N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\leq N\).
For any integer \(N\), let \(\mathcal{C}_m^{\geq N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\geq N\).
Observe that if \(P^{\cdot}\) has level \(\ell\), then \(P^{\cdot}[1]\) has level \(\ell + 1\), and that \(P^{\cdot}[-1]\) has level \(\ell - 1\).
\asilata{The directions of the shifts are a mess.}
\begin{proposition}\label{prop:standard-heart}
  The category \(\mathcal{A}_m\) is abelian.
  Furthermore, it is the heart of a bounded \(t\)-structure on \(\mathcal{C}_m\), which we call the \emph{standard \(t\)-structure} on \(\mathcal{C}_m\).
\end{proposition}
\asilata{Find a reference for this and possibly a cleaner statement.}
